{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Edited on experiment.

\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing a specific challenge of a single,
target tracking problem. Thus each of them should have different value
for the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we empirically
found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate as $0.12$
for $R_{t}^{L}$.

We tuned the number of particles in the particle filter to $1000$ after carrying out experiments, 
The re-sampling is only performed when the \textit{efficient number of samples} ($	\hat{N}_{eff} \approx (\sum_{p=1}^{P}w_{p}^{2})^{-1}
$) is lower than a pre-defined threshold. This way, we can continuously keep reasonable variance among particles.
\begin{equation}
	\label{eq:Neff_PF}
\end{equation}

@@

\textbf{Performance on UAV123 Dataset.}  We compared the performance
of the proposed tracking algorithm with those of the state-of-the-art
high speed tracking algorithms in the \textit{Precision} and
\textit{Success\:Rate} metrics. In precision, we rank the trackers based on the precision numbers at
20 pixels whereas in the success rate plots, trackers are
ranked based on area under curve (AUC) scores.

\begin{comment}
{\it Burak: What do mean by the following sentence? We had graphs
  about precision, but I don't see any tables or anything else to rank
  the algorithms based on the precision at 20 pixels.}

{\it YoungWoo : Trackers are ranked in the legend in the graphs - the numbers next 
to each tracker is precision at 20 px and AUC for the success rate. It is how people rank
trackers in precision and success plots. I agree with you that we can have an additional table. Let me know what
you think about it now.} 
\end{comment}

\begin{comment}
{\it Burak: After you remove some of the trackers, replace that number
  with ``some'' at the below as well as removing their names from the
  following paragraph.}

{\it YoungWoo :  I thought we were going to do that tomorrow. I have generated figures and 
I can easily remove any ones. SRDCF and MEEM are the top two as of now. I am working on removing them as of now. Please 
consider that we do not have SRDCF and MEEM while you are editing the results section.}
\end{comment}
We compare our tracker to other high-speed ($\geq$300 fps)
state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and MOSSE\cite{bolme2010visual,henriques2015high}. Also, five relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient}, MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and
OAB \cite{zhang2012robust}. Fig.~\ref{fig:UAV123_OTB100_DATASET} shows the results on the UAV123
dataset.

{\it Burak: I will re-write the text at below after you clean up the graphs.}

{\it E}nKCF outperformed other, high-speed tracking methods by
$3\%$-$15\%$ at 20 pixels precision metric whereas it is only $5\%$
worse than SAMF, DSST and Struck on the same dataset although it is
$10$-$20$ times faster than these trackers. On the other hand, the
{\it E}nKCF does a decent job on approximating the scale of the target
in highly efficient manner. This is proved by the fact that it ranks
second best tracker in terms of \textit{area under curve} (AUC) value
for the success rate plot. It outperforms the high speed trackers by
about $20\%$-$25\%$ in AUC metric. Interestingly, it performs even
better than most of the low speed trackers. For instance, it
outperforms Struct and DSST by $5\%$ and $10\%$ while running at more
than $30$ and $10$ times larger operation rate.

>>>>

\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing a specific challenge of a single,
target tracking problem. Thus each of them should have different value
for the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.6$, $0.4$, and
$0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate
as $0.12$ for $R_{t}^{L}$. For the particle filter, we empirically set
the number of particles to $1000$ to balance the run-time performance
and accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

@@

\textbf{Performance on UAV123 Dataset.}  We compared the performance
of the proposed tracking algorithm with those of the state-of-the-art
high speed tracking algorithms in the \textit{Precision} and
\textit{Success\:Rate} metrics. In precision, we rank the trackers
based on the precision numbers at 20 pixels whereas in the success
rate plots, trackers are ranked based on area under curve (AUC)
scores. The tracking algorithms used for the comparison include ones
in high-speed ($\geq$300 fps), i.e., KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50), i.e., SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}.

Figure \ref{fig:UAV123_OTB100_DATASET} shows the results on the UAV123
dataset. {\it E}nKCF outperformed most of the high-speed tracking
methods by $3\%$-$15\%$ at 20 pixels precision metric. Three
algorithms, SAMF, DSST, and Struck did about 5\% better than ours in
accuracy, but 10-20\% slower than ours. For the scale adaptation, {\it
  E}nKCF did second best in terms of \textit{area under curve} (AUC)
value for the success rate plot. It outperformed other tracking
methods in high-speed by about $20\%$-$25\%$ in AUC metric. In
addition, it performed even better than those algorithms that are
slow, but a bit better in precision. For example, for AUC, {\it E}nKCF
outperformed Struct and DSST by $5\%$ and $10\%$ while running at more
than $10$ and $30$ times faster.
